---
title: "awardFindR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{awardFindR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`search_awards` is meant to be the top-level function for interacting with grant database search functions.

## Load awardFindR
```{r}
library(awardFindR)
```

## Simple keyword search, single source
```{r, message=FALSE}
nsf <- search_awards(keywords="illicit", sources="nsf", from_date="2023-01-01")
str(nsf)
```

## Multiple sources and keywords, specific date range
```{r, message=FALSE}
nsf_and_nih <- search_awards(keywords=c("ontological", "audio recordings"), sources=c("nsf", "nih"), from_date="2018-01-01", to_date="2018-02-01")
table(nsf_and_nih$source)
unique(nsf_and_nih$keyword)
```

For more than a few keywords, you can specify an external simple csv file. If you specify a .csv file path for `keywords`, the file should be a list of keywords, one string per line. For example:
```
qualitative data
qualitative analysis
case study
case studies
```
